---
title: "Meaningfulness of STS Clustering"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---
## Importing variety of time series

Importing S&P 500 Daily time series:

```{r}
spx <- read.csv('../data/spx_daily_11-21.csv')
spx <- rev(spx[,2])
idx = 1:length(spx)
sprintf("Length: %d",length(spx))
plot(idx,spx,type='l')
```

Importing minimum temperature data set:

```{r}
min_daily_temp <- read.csv('../data/daily-minimum-temperatures-in-melbourne.csv')
min_daily_temp <- min_daily_temp[,2]
idx = 1:length(min_daily_temp)
sprintf("Length: %d",length(min_daily_temp))
plot(idx,min_daily_temp,type='l')
```

Importing german DAX alltime:

```{r}
char_dax_alltime <- read.csv('../data/dax_alltime.csv',sep=',')
char_dax_alltime <- char_dax_alltime[,2]
dax_alltime = as.double(char_dax_alltime)
idx = 1:length(dax_alltime)
for (i in idx) {
  if (is.na(dax_alltime[i])||is.nan(dax_alltime[i])) {
    dax_alltime[i] <- dax_alltime[i-1]
  }
}
sprintf("Length: %d",length(dax_alltime))
plot(idx,dax_alltime,type='l')
```

Importing Bitcoin alltime:

```{r}
char_bitcoin_alltime <- read.csv('../data/bitcoin_alltime.csv')
char_bitcoin_alltime <- char_bitcoin_alltime[,2]
bitcoin_alltime = as.double(char_bitcoin_alltime)
idx = 1:length(bitcoin_alltime)

for (i in idx) {
  if (is.na(bitcoin_alltime[i]) || is.nan(bitcoin_alltime[i])) {
    bitcoin_alltime[i] <- bitcoin_alltime[i-1]
  }
}
sprintf("Length: %d",length(bitcoin_alltime))
plot(idx,bitcoin_alltime,type='l')
```

Importing hydraulic pressure data set:

```{r}
hydraulic <- read.csv('../data/PS1.csv')
hydraulic <- hydraulic[,2]
idx = 1:length(hydraulic)
for (i in idx) {
  if (is.nan(hydraulic[i]) || is.na(hydraulic[i])) {
    hydraulic[i] <- hydraulic[i-1]
  }
}
sprintf("Length: %d",length(hydraulic))
plot(idx,hydraulic,type='l')
```

Importing Beijing O3 in air concentration (quality):

```{r}
air_quality <- read.csv('../data/PRSA_Data_Dingling_20130301-20170228.csv')
air_quality <- air_quality[,11]
idx = 1:length(air_quality)
for (i in idx) {
  if (is.nan(air_quality[i]) || is.na(air_quality[i])) {
    air_quality[i] = air_quality[i-1]
  }
}
sprintf("Length: %d",length(air_quality))
plot(idx,air_quality,type='l')
```

### Setting hyper parameters for experimental run

```{r}
source("random_walk.R")
# number of iterations of meaningfulness calculation to average over.
n <- 10
# size of cluster set to be calculated for within/between set cluster distance.
r <- 10

ks <- c(3,5,7,11)
ws <- c(8,16,32)

norm_methods <- c("none","center", "scale", "range");
dist_metrics <- c("eukl")
cluster_algos <- c("kmeans","agglo","gmm")


##### unification #####
unify <- TRUE

##### clustering algorithm #####
cluster_algo <- cluster_algos[3]

############ unchanged hyperparameters ############
dist_metric <- dist_metrics[1]
seed_ <- 0
dim_red <- TRUE
norm_method <- norm_methods[1]
# reduces de sampling size of the random sampled subsequences that are used for whole clustering
# if false the random samples matrix has the same height as the sts matrix
reduced_sampling <- TRUE
###################################################

##### time series #####
## [spx, min_daily_temp, dax_alltime, bitcoin_alltime, hydraulic, quality]
target_ts <- spx
opposing_ts <- create_random_walk(target_ts,seed_)

```

### Finally calculate Meaningfulness

```{r}
print('Experiment settings:')
print('')
sprintf("n:                                           %d",n)
sprintf('r:                                           %d',r)
sprintf('Normalizer:                                  %s',norm_method)
sprintf('Distance metric:                             %s',dist_metric)
sprintf('Clustering algorithm:                        %s',cluster_algo)
sprintf('Reduced sampling size for whole clustering:  %s',reduced_sampling)
sprintf('PCA:                                         %s',dim_red)
sprintf('Unified hyperparameters:                     %s',unify)

plot(1:length(target_ts),target_ts, type = 'l')
title("Target time series")

plot(1:length(opposing_ts),opposing_ts,type = 'l')
title("Opposing time series")

print("")
print("Results:")

l_ks <- length(ks)
l_ws <- length(ws)

meaningfulness_table <- matrix(0, nrow = (l_ks*l_ws), ncol = 4)
meaningfulness_plot <- matrix(0, nrow=length(ws), ncol = (length(ks)*2))

```

```{r}
source("random_walk.R")
source("meaningfulness_calculations.R")
i <- 1
j <- 1
for (w in 1:length(ws)) {
  j <- 1
  for (k in 1:length(ks)) {
    m <- calculate_meaningfulness(target_ts,opposing_ts,n,ks[k],ws[w],r,dist_metric,norm_method,cluster_algo,reduced_sampling,dim_red,unify,seed_)
    m <- round(m, 2)
    meaningfulness_table[i,] <- c(ws[w],ks[k],m[1],m[2])
    meaningfulness_plot[w,j] <- m[1]
    meaningfulness_plot[w,(j+1)] <- m[2]
    i <- i+1
    j <- j+2
  }
}
 

df_meaningfulness <- data.frame(w=meaningfulness_table[,1],
                                k=meaningfulness_table[,2],
                                sts=meaningfulness_table[,3],
                                whole=meaningfulness_table[,4])
df_meaningfulness

for (i in 1:length(ws)) {
  df_meaningfulness_plot <- data.frame(meaningfulness=meaningfulness_plot[i,],
                                k=rep(c("3","5","7","11"),each=2),
                                algorithm=c("sts","whole"))
  str <- paste("w =",ws[w])
  print(ggplot(df_meaningfulness_plot,                                      
       aes(x = k,
           y = meaningfulness,
           fill = algorithm)) +
    geom_bar(stat = "identity",
             position = "dodge") +
    labs(title = str))
  Sys.sleep(1)
}

``` 

### Calculating average meaningfulness over all time series

```{r}
source("random_walk.R")
source("meaningfulness_calculations.R")

## [spx, min_daily_temp, dax_alltime, bitcoin_alltime, hydraulic, quality]


i <- 1
j <- 1

for (w in 1:length(ws)) {
  j <- 1
  for (k in 1:length(ks)) {
    m <- calculate_meaningfulness(spx, create_random_walk(spx, seed_), n,ks[k],ws[w],r,dist_metric,norm_method,cluster_algo,reduced_sampling,dim_red,unify,seed_)
    print(paste('Calculated: spx_short',m))
    
    m_ <- calculate_meaningfulness(min_daily_temp, create_random_walk(min_daily_temp, seed_), n,ks[k],ws[w],r,dist_metric,norm_method,cluster_algo,reduced_sampling,dim_red,unify,seed_)
    m <- m + m_
    print(paste('Calculated: min_daily_temp',m_))
    
    m_ <- calculate_meaningfulness(dax_alltime, create_random_walk(dax_alltime, seed_), n,ks[k],ws[w],r,dist_metric,norm_method,cluster_algo,reduced_sampling,dim_red,unify,seed_)
    m <- m + m_
    print(paste('Calculated: dax_alltime',m_))
    
    m_ <- calculate_meaningfulness(bitcoin_alltime, create_random_walk(bitcoin_alltime, seed_), n,ks[k],ws[w],r,dist_metric,norm_method,cluster_algo,reduced_sampling,dim_red,unify,seed_)
    m <- m + m_
    print(paste('Calculated: bitcoin_alltime',m_))
    
    m_ <- calculate_meaningfulness(hydraulic, create_random_walk(hydraulic, seed_), n,ks[k],ws[w],r,dist_metric,norm_method,cluster_algo,reduced_sampling,dim_red,unify,seed_)
    m <- m + m_
    print(paste('Calculated: hydraulic',m_))
    
    #m_ <- calculate_meaningfulness(air_quality, create_random_walk(air_quality, seed_), n,ks[k],ws[w],r,dist_metric,norm_method,cluster_algo,reduced_sampling,dim_red,unify,seed_) 
    #m <- m + m_
    #print(paste('Calculated: air_quality',m_))
    
    m <- round(m/5, 2)
    print(paste('Final',m))
    print('')
    print('')

    meaningfulness_table[i,] <- c(ws[w],ks[k],m[1],m[2])
    meaningfulness_plot[w,j] <- m[1]
    meaningfulness_plot[w,(j+1)] <- m[2]
    i <- i+1
    j <- j+2
  }
}
 

df_meaningfulness <- data.frame(w=meaningfulness_table[,1],
                                k=meaningfulness_table[,2],
                                sts=meaningfulness_table[,3],
                                whole=meaningfulness_table[,4])
df_meaningfulness

for (i in 1:length(ws)) {
  df_meaningfulness_plot <- data.frame(meaningfulness=meaningfulness_plot[i,],
                                k=rep(c("3","5","7","11"),each=2),
                                algorithm=c("sts","whole"))
  str = paste("w =",ws[w])
  print(ggplot(df_meaningfulness_plot,                                      
       aes(x = k,
           y = meaningfulness,
           fill = algorithm)) +
    geom_bar(stat = "identity",
             position = "dodge") +
    labs(title = str))
  Sys.sleep(1)
}

``` 

